\documentclass[10pt]{article}
\usepackage{amsmath,amsfonts,amssymb,amsthm}
\usepackage{graphicx,mathrsfs}
\pagestyle{empty}

\usepackage[left=2cm, top=2cm, bottom = 2cm, right=2cm, nohead, nofoot]{geometry}


\begin{document}

\begin{center}
{\Large\bf  Homework - MTH 357}\\
\vspace{.1in}


\end{center}

\noindent Instructions:  
Homework is to be neat and organized.  \textbf{If it's messy it's wrong.} Answers without the necessary supporting work are worth 0.   You may discuss problems with others but must always produce your own work and write your own solutions.  Copying someone else's homework is considered cheating.\\


\noindent \textbf{HW9, due 12/7}\\
\begin{enumerate}
\item  Find the Fourier integral representation of the solution, $u(x,t)$, to the heat equation on a metal bar of infinite length in both directions, with arbitrary $c$ and $u(x,0)=f(x)=e^{-|x|}$. Simplify the inner integral
\item Use Mathematica to plot your solution from \#1 (with $c=1$), plotting $u(x,0)$, $u(x,1)$, and $u(x,2)$ on the same graph.
\item  Find the Fourier integral representation of the solution, $u(x,t)$, to the heat equation on a half-infinite metal bar of, with arbitrary $c$, $u(0,t)=0$, and $u(x,0)=f(x)=Boole[0<x<2](1-(x-1)^2)$. Simplify the inner integral
\item Use Mathematica to plot your solution from \#3 (with $c=1$), plotting $u(x,0)$ and $u(x,0.5)$ on the same graph.
\begin{enumerate}
\item As usual, you may use Mathematica for integrals as long as you turn in what you're using.
\item If you don't simplify the inner integrals and use them for parts 2 and 4, Mathematica will likely take too long when creating your plots. 
\item Even with the simplified inner integrals, the plots can take 10-30 seconds to complete. 
\item Feel free to borrow syntax from 12.7.nb, which is posted on Canvas.
\end{enumerate}
\end{enumerate}







\end{document}
